---
name: Kate Saunders
position: "Postdoctoral Researcher"
address: "Delft Institute of Applied Mathematics, TU Delft"
phone: +31 6 3374 7624
# www: mariecurie.com
email: "K.R.Saunders@tudelft.nl"
twitter: katerobsau
github: katerobsau
# linkedin: mariecurie
date: "`r format(Sys.time(), '%B %Y')`"
output: vitae::awesomecv
# headcolor: '#9bcf2f'
---


```{r setup, include=FALSE}
library(tidyverse)
library(vitae)
knitr::opts_chunk$set(echo = FALSE)
```

# About me

 * Current research is in statistical post-processing
* Core focus is on improving probabilistic forecasts of extreme weather events
 * PhD research was in extreme value theory
 * Core PhD focus was on modelling rainfall extremes in continuous space with dependence
 * Applications considered in the thesis helped to improve our understanding of rainfall extremes in Australia
 * Passionate about R programming and data visualisation


# Employment
```{r}
tribble(
  ~ role, ~ company, ~ loc, ~ dates, ~ details,
  "Posdoctoral Researcher", "Delft University of Technology", "Deflt, Netherlands", "Oct. 2018 - Present", "Collaborating on a joint project with Koninklijk Nederlands Meteorologisch Instituut (KNMI)",
    "Posdoctoral Researcher", "Delft University of Technology", "Deflt, Netherlands", "Oct. 2018 - Present", "Research Interests: Post-processing for extreme events, compound events, modelling extremal dependece using covariates",
  
   "Graduate Researcher", "Commonwealth Scientific Institue of Technology (CSIRO)", "Melbourne, Australia", "Feb. 2012 - Feb. 2014", "Research Interests: natural disaster modelling, floods, tsnumais, sea level rise, computational fluid dynamics"
 
  #  "Teaching Associate", "Monash University", "Caulfield & Clayton, Australia", "S1 2016 - Present", "Business forecasting (ETF3231/ETF5231)",
  # "Teaching Associate", "Monash University", "Caulfield & Clayton, Australia", "S1 2016 - Present", "Mathematics for business (ETF2700)",
  # "Teaching Associate", "Monash University", "Caulfield & Clayton, Australia", "S1 2016 - Present", "Data modelling and computing (ETC1010)",
  # "Research Assistant", "Monash University", "Clayton, Australia", "Jan. 2016 - Present", "Supervisors include Rob Hyndman, Dianne Cook, and George Athanasopoulos.",
  # "Research Assistant", "Monash University", "Clayton, Australia", "Jan. 2016 - Present", "Consulting projects with DiabetesLab, Tennis Australia, Monash University and Huawei.",
  # "Research Assistant", "Monash University", "Clayton, Australia", "Jan. 2016 - Present", "Contributed to the development of numerous open source R packages.",
  # "Volunteer", "Rotaract", "Monash, Australia", "Feb. 2013 - Nov. 2016", "Development and maintenance of club website and online services.",
  # "Volunteer", "Rotaract", "Monash, Australia", "Feb. 2013 - Nov. 2016", "Organising and hosting fundraisers.",
  # "Student Ambassador", "Google", "Sydney, Australia", "Feb. 2015 - Nov. 2015", "Supported Google's presence on campus with events and media.",
  # "Data Mining (Internship)", "iSelect", "Cheltenham, Australia", "Feb. 2015 - Mar. 2015", "Improved business data and issue reporting with interactive visualisations, and model-based anomaly detection.",
  # "Fresh Produce", "Coles", "Rowville, Australia", "Oct. 2010 - Nov. 2015", "Food preparation & display, first aid, staff training and customer assistance."
) %>% 
  detailed_entries(company, dates, role, loc, details)
```

# Education
```{r}
tribble(
  ~ uni, ~ degree, ~ loc, ~ dates, ~ details,
  
  "Doctor of Philosophy", "The University of Melbourne", "Melbourne, Australia", "Mar. 2014 - Oct. 2018", "Thesis Advisors: Prof. Peter Taylor, Prof. David Karoly and Dr. Alec Stephenson",
  "Doctor of Philosophy", "The University of Melbourne", "Melbourne, Australia", "Mar. 2014 - Oct. 2018", "Thesis Title: An Investigation of Australian Rainfall using Extreme Value Theory",
  "Doctor of Philosophy", "The University of Melbourne", "Melbourne, Australia", "Mar. 2014 - Oct. 2018", "Research Interests: Extreme Value Theory, Statistics, Max-stable Processes, Rainfall Extremes, Extremal Dependence, Quality Control",
  
   "Bachelor of Science (Honours I in Mathematics)", "The University of Queensland", "Brisbane, Australia", "Jul. 2010 - Jun. 2011", "Thesis advisors: Prof. Tony Roberts",
  "Bachelor of Science (Honours I in Mathematics)", "The University of Queensland", "Brisbane, Australia", "Jul. 2010 - Jun. 2011", "Thesis title: Mean first passage time for discrete periodic networks",
  
  "Bachelor of Science", "The University of Queensland", "Brisbane, Australia", "Feb. 2007 - Jun. 2010", "Major in mathematics"
  #,
  # "Bachelor of Science", "The University of Queensland", "Brisbane, Australia", "Feb. 2007 - Jun. 2010", "SOMETHING ABOUT GRADES"
 
) %>% 
  detailed_entries(degree, dates, uni, loc, details)
```

# Publications
```{r}
tribble(
  ~ authors, ~ year, ~ title, ~ journal, ~ doi,
 "A.G. Stephenson, K. Saunders and L. Tafakori", "2018", "The Winning Entry for the EVA2017 Competition for Spatiotemporal Prediction of Extreme Rainfall using Generalized Extreme Value Quantiles", "Extremes", "DOI: 10.1007/s10687-018-0321-0",
 
 "K. Saunders, A.G. Stephenson, P.G. Taylor, and D. Karoly", "2017", "The spatial distribution of rainfall extremes and the influence of El Niño Southern Oscillation", "Weather and Climate Extremes", "DOI: 10.1016/j.wace.2017.10.001",

"P. Bayliss, K. Saunders, L. Dutra, L. Melo, J. Hilton, M. Prakash, F. Woolard", "2016", "Assessing sea level rise risks to coastal floodplains in the Kakadu Region, Northern Australia, using a tidally-driven hydrodynamic model", "Marine and Freshwater Research", "DOI: 10.1071/MF16049", 
 
"K. Saunders, M. Prakash, P.W. Cleary and M. Cordell", "2014", "Application of Smoothed Particle Hydrodynamics for Modelling Gated Spillway Flows", "Applied Mathematical Modelling", 
"DOI: 10.1016/j.apm.2014.05.008"

 ) %>% 
  detailed_entries(authors, year, title, journal, doi)
```

\newpage

<!-- # Relevant Skills -->
<!-- ```{r} -->
<!-- cvskill("Data Analysis", c("Visualisation", "Data Cleaning", "Forecasting", "Modelling", "Communication", "Inference", "Machine Learning", "Web Scraping")) -->
<!-- cvskill("Programming", c("R", "Python", "SQL", "Java", "C", "C++", "HTML/CSS", "TeX", "MATLAB")) -->
<!-- ``` -->

<!-- # Awards & Achievements -->
<!-- ## Awards -->
<!-- ```{r} -->
<!-- tribble( -->
<!--   ~ award, ~ from, ~ year, -->
<!--   "Commerce Dean's Honour", "Monash", "2017", -->
<!--   "Commerce Dean's Commendation", "Monash", "2016", -->
<!--   "Science Dean’s List", "Monash", "2014-2016", -->
<!--   "International Institute of Forecasters Award", "IIF", "2014", -->
<!--   "Rotary Youth Leadership Award", "Rotary", "2013" -->
<!-- ) %>% -->
<!--   brief_entries(award, year, from) -->
<!-- ``` -->

<!-- ## Scholarships -->
<!-- ```{r} -->
<!-- tribble( -->
<!--   ~ scholarship, ~ from, ~ year, -->
<!--   "Econometrics Honours Memorial Scholarship", "Monash", "2017", -->
<!--   "Monash Community Leaders Scholarship", "Monash", "2015 & 2016", -->
<!--   "Mitcham Rotary Scholarship", "Rotary", "2011 & 2012" -->
<!-- ) %>% -->
<!--   brief_entries(scholarship, year, from) -->
<!-- ``` -->


<!-- ## Competitions -->
<!-- ```{r} -->
<!-- tribble( -->
<!--   ~ competition, ~ from, ~ year, -->
<!--   "UseR! 2018 Datathon Champion", "UseR!", "2018", -->
<!--   "RMIT SBITL Analytics Competition Champion", "RMIT", "2017", -->
<!--   "RMIT SBITL Analytics Competition Champion", "RMIT", "2016" -->
<!-- ) %>% -->
<!--   brief_entries(competition, year, from) -->
<!-- ``` -->
