---
name: Kate Saunders
position: "Postdoctoral Researcher"
address: "Delft Institute of Applied Mathematics, TU Delft"
phone: +31 6 3374 7624
# www: mariecurie.com
email: "K.R.Saunders@tudelft.nl"
twitter: katerobsau
github: katerobsau
# linkedin: mariecurie
date: "`r format(Sys.time(), '%B %Y')`"
output: vitae::awesomecv
# headcolor: '#9bcf2f'
---


```{r setup, include=FALSE}
library(tidyverse)
library(vitae)
knitr::opts_chunk$set(echo = FALSE)
```

# About me

 * Current research is in statistical post-processing and compound events
* Core focus is on improving probabilistic forecasts of extreme weather events
 * PhD research was in extreme value theory
 * Core PhD focus was on modelling rainfall extremes in continuous space with dependence
 * Applications considered in the thesis helped to improve our understanding of rainfall extremes in Australia
 * Passionate about R programming and data visualisation


# Employment
```{r}
tribble(
  ~ role, ~ company, ~ loc, ~ dates, ~ details,
  
  "Posdoctoral Researcher", 
  "Delft University of Technology", 
  "Deflt, Netherlands", 
  "Oct. 2018 - Present", 
  "Collaborating on a joint project with Koninklijk Nederlands Meteorologisch Instituut (KNMI)",
    
  "Posdoctoral Researcher", 
  "Delft University of Technology", 
  "Deflt, Netherlands", 
  "Oct. 2018 - Present", 
  "Research Interests: Post-processing for extreme events, compound events, modelling extremal dependence using covariates",
  
   "Graduate Researcher", 
  "Commonwealth Scientific Institue of Technology (CSIRO)", 
  "Melbourne, Australia", 
  "Feb. 2012 - Feb. 2014", 
  "Research Interests: natural disaster modelling, floods, tsnumais, sea level rise, computational fluid dynamics"
  
) %>% 
  detailed_entries(company, dates, role, loc, details)
```

# Education
```{r}
tribble(
  ~ uni, ~ degree, ~ loc, ~ dates, ~ details,
  
  "Doctor of Philosophy", "The University of Melbourne", "Melbourne, Australia", "Mar. 2014 - Oct. 2018", "Thesis Advisors: Prof. Peter Taylor, Prof. David Karoly and Dr. Alec Stephenson",
  "Doctor of Philosophy", "The University of Melbourne", "Melbourne, Australia", "Mar. 2014 - Oct. 2018", "Thesis Title: An Investigation of Australian Rainfall using Extreme Value Theory",
  "Doctor of Philosophy", "The University of Melbourne", "Melbourne, Australia", "Mar. 2014 - Oct. 2018", "Research Interests: Extreme Value Theory, Statistics, Max-stable Processes, Rainfall Extremes, Extremal Dependence, Quality Control",
  
   "Bachelor of Science (Honours I in Mathematics)", "The University of Queensland", "Brisbane, Australia", "Jul. 2010 - Jun. 2011", "Thesis advisors: Prof. Tony Roberts",
  "Bachelor of Science (Honours I in Mathematics)", "The University of Queensland", "Brisbane, Australia", "Jul. 2010 - Jun. 2011", "Thesis title: Mean first passage time for discrete periodic networks",
  
  "Bachelor of Science", "The University of Queensland", "Brisbane, Australia", "Feb. 2007 - Jun. 2010", "Major in mathematics"
  #,
  # "Bachelor of Science", "The University of Queensland", "Brisbane, Australia", "Feb. 2007 - Jun. 2010", "SOMETHING ABOUT GRADES"
 
) %>% 
  detailed_entries(degree, dates, uni, loc, details)
```

# Publications
```{r}
tribble(
  ~ authors, ~ year, ~ title, ~ journal, ~ doi,
  
  "K.R. Saunders, A.G. Stephenson, AG and D.J. Karoly", "2019",
  "A Regionalisation Approach for Rainfall based on Extremal Dependence",
  "Extremes (in submission)", "Preprint: https://arxiv.org/abs/1907.05750",
  
    "K.R. Saunders", "2018",
  "An Investigation of Australian Rainfall Using Extreme Value Theory",
  "PhD Thesis", "Identifier: http://hdl.handle.net/11343/220318",
  
 "A.G. Stephenson, K. Saunders and L. Tafakori", "2018", "The Winning Entry for the EVA2017 Competition for Spatiotemporal Prediction of Extreme Rainfall using Generalized Extreme Value Quantiles", "Extremes", "DOI: 10.1007/s10687-018-0321-0",
 
 "K. Saunders, A.G. Stephenson, P.G. Taylor, and D. Karoly", "2017", "The Spatial Distribution of Rainfall Extremes and the Influence of El Niño Southern Oscillation", "Weather and Climate Extremes", "DOI: 10.1016/j.wace.2017.10.001",

"P. Bayliss, K. Saunders, L. Dutra, L. Melo, J. Hilton, M. Prakash, F. Woolard", "2016", "Assessing Sea Level Rise Risks to Coastal Floodplains in the Kakadu Region, Northern Australia, using a tidally-driven hydrodynamic model", "Marine and Freshwater Research", "DOI: 10.1071/MF16049", 
 
"K. Saunders, M. Prakash, P.W. Cleary and M. Cordell", "2014", "Application of Smoothed Particle Hydrodynamics for Modelling Gated Spillway Flows", "Applied Mathematical Modelling", 
"DOI: 10.1016/j.apm.2014.05.008"

 ) %>% 
  detailed_entries(authors, year, title, journal, doi)
```

# Teaching Experience
```{r}
tribble(
  ~ position, ~ faculty, ~ location, ~ year, ~ details,
  
  "Lecturer",
  "Deflt Institute of Applied Mathematics",
  "TU Deflt",
  "Current",
  "WI2180LR-II Probability and Statistics",
  
  "Sessional Tutor",
  "School of Mathematics and Statistics",
  "The University of Melbourne",
  "2014 -- 2015",
  "MAST20005 Statistics, MAST20004 Probability for statistics, MAST10006 Calculus 2",
  
  # "College Tutor",
  # "Newman College", 
  # "The University of Melbourne",
  # "2015",
  # "Probability and Statistics tutor for undergraduate students",
  # 
  "Sessional Tutor",
  "School of Mathematics and Physics",
  "The University of Queensland",
  "2007 -- 2011",
  "MATH1061 Discrete Mathematics, MATH1051 Calculus and Linear Algebra,
  MATH1050 Mathematical Foundations, MATH1040 Basic Mathematics"
  
) %>% 
  detailed_entries(faculty, year, position, location, details)

```

# Invited talks

```{r}
tribble(
 ~ type, ~ year, ~ where, ~ topic,
 
  "Extremes TiDE Seminar Series", 
  "2019",
  "Tilburg University, Netherlands",
  "A Regionalisation Approach for Extremes"
 
) %>% 
  detailed_entries(topic, year, type, where) 
```
<!-- Newcastle upcoming -->
<!-- Delft/Statistics Seminar upcoming -->

# Supervision Experience

```{r}
tribble(
 ~ type, ~ year, ~ where, ~ topic,
 
"Undergraduate Student",#" (8 week project)", 
"2016",
"The University of Melbourne",
"Project Topic: Identifying spurious inhomogeneities in daily rainfall observations",

"Undergraduate Student", # (4 week project)", 
"2012",
"CSIRO",
"Project Topic: A sensitivity analysis of tsunami inundation using a shallow water solver"
) %>% 
  detailed_entries(topic, year, type, where) 
```

# Other Academic Activities

## Workshop Organisation

```{r}
tribble(
  ~with, ~when, ~what, ~why,
  
  # "KNMI and TU Delft workshop on post-processing",
  # "(upcoming in 2019)",
  # "TU Delft",
  # "A workshop prom",
  # 
  "Climate and Energy College Retreat",
  "2018",
  "Hidden Vale, Victoria",
  "A workshop to promote knowledge sharing between PhD students",
  
  "Applied Probability Group Retreat",
  "2017",
  "Lorne, Victoria",
  "An internal workshop to share new research ideas in applied probability"
  
  ) %>% 
   detailed_entries(with = with, when = when, what = what, why = why)
```

## Journal Refereering
Spatial Statistics, Stochastic Networks, Extremes, Environmetrics

## Promotion of Women in STEM 

```{r}
tribble(
  ~with, ~when, ~what, ~why,
  
  "An Introduction to Web Scraping using Rvest",
  "2019",
  "Invited presentation for R-Ladies Rotterdam",
  "R-Ladies’ is a diversity initiative, whose aim is to help empower underrepresented minorities within the R community.",
  
  "Women in mathematics panel discussion on affirmitive action",
  "2016",
  "Event Organiser and Panel Chair",
  "Internation Womens' Day Event #BeBoldForChange",

# The School of Mathematics and Statistics made the bold decision last year to advertise and hire female only candidates. To celebrate this decision we will be holding a Q & A in the School of Mathematics and Statistics.
# In the Q & A we hope to bring light to some of the gender issues that were drivers behind the hiring decision, discuss the legalities and give people the opportunity to ask questions. 
  
  "A celebration of Dr. Alison Harcourt (Order of Australia)",
  "2015",
  "Event Joint Organiser",
  "Internation Womens' Day Event #MakeItHappen"
  
) %>% 
   detailed_entries(with = with, when = when, what = what, why = why)
```
\newpage

## Mentoring
```{r}
tribble(
  ~with, ~when, ~what, ~why,
  
  "Grabbing your Audience's Attention: Advice on Giving Talks",
  "2019",
  "ACEMS Seminar Series",
  "Mentoring talk shared live across ACEMS university nodes",
  
  "ACEMS Mentoring Program",
  "2019",
  "Mentor",
  "Paired with an early stage PhD Student in Statistics at Monash University"
  
) %>% 
   detailed_entries(with = with, when = when, what = what, why = why)
```

## Committee Positions
```{r}
tribble(
  ~with, ~when, ~where, ~why, ~what,
  
  "Student President",
  "2015 -- 2016",
  "University of Melbourne",
  "Events run include: National Science Week Events, Careers Panel, Social Events",
  "Mathematics and Statistics Student Society (STAMPS)"
  
) %>% 
   detailed_entries(with = with, when = when, where = where, what = what, why = why)
```

# Outreach & Science Communication

## Art Exhibition

```{r}
tribble(
  ~with, ~when, ~what, ~why,
  
  "ClimArt",
  "2019",
  "R Package",
  "Produced code that visualises climate observations and how these observations are changing. These visualisations are used in an exhibition called Climate Change versus Art."
  
) %>% 
   detailed_entries(with = with, when = when, what = what, why = why)
```

## Popular Science Articles
```{r}
tribble(
  ~ authors, ~ year, ~ title, ~ blog, ~ stats,
  
  "K. Saunders and A.G. Stephenson", 
  "2017",
  "Is Usain Bolt the greatest athlete of all time? That's not what the numbers say",
  "The Conversation", 
   # \href{https://theconversation.com/is-usain-bolt-the-greatest-athlete-of-all-time-thats-not-what-the-numbers-say-82212} 
  "Article statistics: 20,609 Readers, 275 Shares", #19 Tweets, 
  
  "K. Saunders, D. Karoly and P.G. Taylor", 
  "2015",
  # \href{https://theconversation.com/explainer-was-the-sydney-storm-once-in-a-century-40824} 
  "Explainer: was the Sydney storm ‘once-in-a-century’?", 
  "The Conversation",
  "Article statistics: 8591 Readers, 80 Shares" #24 Tweets,
  
) %>% 
  detailed_entries(authors, year, title, blog, stats)  
```  

## Schools

```{r}
tribble(
  ~with, ~when, ~what, ~why,
  
  "Maths like a Mathematician",
  "2015 - 2017",
  "ACEMS Mathscraft",
  "Initiative to work with schools to teach mathematical style thinking to students",
  
  "Mathematicians in Schools",
  "2012 - 2013",
  "Partner school Mentone Girls' Grammar School",
  "Presented my research in schools to help students understand how maths is used in the real world"
  
) %>% 
   detailed_entries(with = with, when = when, what = what, why = why)
```

# Scholarships and Awards
```{r}
tribble(
 ~ award, ~ from, ~ amount, ~ dates, ~ details,
  
 "Laureate Fellowship: Postgraduate Researcher Award",
 "The University of Melbourne",
 "$30,000 AUD per annum (~ €18,800 tax free)",
 "2014 -- 2018",
 "Awarded in lieu of the Australian Postgraduate Award ($25,000 AUD per annum)",
 
  "Postgraduate Top Up Scholarship",
  "CSIRO",
  "$10,000 per annum (~ €6,265 tax free)",
  "2015 -- 2018",
  "Awarded to outstanding graduates to undertake postgraduate research",
  
  "Science Abroad Travelling Scholarship",
  "The University of Melbourne",
  "$1,500 AUD in total (~ €940 tax free)",
  "2016",
  "Awarded to outstanding graduates to undertake research abroad"
  
# {\bf The University of Queensland} \smallskip \\
# {\em Student Exchange Scholarship} (\$5,000 total) \hfill {2010}\\
# Awarded on the basis of academic merit to support a student exchange abroad \smallskip\\
# {\em Dean's Commendation, Faculty of Science} \hfill{2007 -- 2009} \\
# Awarded all eligible semesters for for academic excellence \smallskip\\ 
# {\em Summer Research Scholarship} (\$2,400 total) \hfill{2009} \\
# Awarded on the basis of academic merit to undertake an 8 week research project

) %>% 
  detailed_entries(amount, dates, award, from, details)  
```  

# Prizes
```{r}
tribble(
 ~ prize, ~ from, ~ year,
  
  "Winner of the Young Statisticians Video Competition",
  "Statistics Society of Australia",
  # "$200 AUD prize (€125)",
  "2017",
  
  "Winning Team of the Data Challenge: Prediction of Extremal Precipitation", 
  "Extreme Value Analysis Conference, Delft, 2017",
   "2017"

) %>% 
  detailed_entries(from, year, prize) 
```

# Affiliations 

* Academic Collaborator with Koninklijk Nederlands Meteorologisch Instituut (KNMI)
* Associate Investigator with Australian Centre of Excellence in Mathematical and Statistical Frontiers (ACEMS)
* German Climate and Energy College (Alumni)
* Women in Mathematics Special Interest Group (WIMSIG)
* Statistical Society of Australia: SSA (Past Member)
* Australian Mathematical Society (Past Member)


<!-- # Referees -->
<!-- Available upon request -->



<!-- # Relevant Skills -->
<!-- ```{r} -->
<!-- cvskill("Data Analysis", c("Visualisation", "Data Cleaning", "Forecasting", "Modelling", "Communication", "Inference", "Machine Learning", "Web Scraping")) -->
<!-- cvskill("Programming", c("R", "Python", "SQL", "Java", "C", "C++", "HTML/CSS", "TeX", "MATLAB")) -->
<!-- ``` -->

<!-- # Awards & Achievements -->
<!-- ## Awards -->
<!-- ```{r} -->
<!-- tribble( -->
<!--   ~ award, ~ from, ~ year, -->
<!--   "Commerce Dean's Honour", "Monash", "2017", -->
<!--   "Commerce Dean's Commendation", "Monash", "2016", -->
<!--   "Science Dean’s List", "Monash", "2014-2016", -->
<!--   "International Institute of Forecasters Award", "IIF", "2014", -->
<!--   "Rotary Youth Leadership Award", "Rotary", "2013" -->
<!-- ) %>% -->
<!--   brief_entries(award, year, from) -->
<!-- ``` -->

<!-- ## Scholarships -->
<!-- ```{r} -->
<!-- tribble( -->
<!--   ~ scholarship, ~ from, ~ year, -->
<!--   "Econometrics Honours Memorial Scholarship", "Monash", "2017", -->
<!--   "Monash Community Leaders Scholarship", "Monash", "2015 & 2016", -->
<!--   "Mitcham Rotary Scholarship", "Rotary", "2011 & 2012" -->
<!-- ) %>% -->
<!--   brief_entries(scholarship, year, from) -->
<!-- ``` -->

<!-- ## Competitions -->
<!-- ```{r} -->
<!-- tribble( -->
<!--   ~ competition, ~ from, ~ year, -->
<!--   "UseR! 2018 Datathon Champion", "UseR!", "2018", -->
<!--   "RMIT SBITL Analytics Competition Champion", "RMIT", "2017", -->
<!--   "RMIT SBITL Analytics Competition Champion", "RMIT", "2016" -->
<!-- ) %>% -->
<!--   brief_entries(competition, year, from) -->
<!-- ``` -->
