---
name: Kate Saunders
position: "Lecturer"
address: "Queensland University of Technology (QUT)"
phone: +61 7 3138 9952
# www: www.webpage.com
email: "kate.r.saunders@qut.edu.au"
twitter: katerobsau
github: katerobsau
# linkedin: linkedin
date: "`r format(Sys.time(), '%B %Y')`"
output: vitae::awesomecv
# headcolor: '#9bcf2f'
---

```{r setup, include=FALSE}
library(tidyverse)
library(vitae)
knitr::opts_chunk$set(echo = FALSE)
```

# About me

 * Primary research interest is in extreme value theory methods as applied to problems in climatology
 * Other research interests include; statistical post-processing, compound event modelling and quality control 
 * Passionate about R programming, data visualisation and data ethics
 * Preference for lecturing into probability and statistics units
 * Postdoctoral research was in improving statistical post-processing methods for compound event forecasts
 * Postgraduate research was in extreme value theory methods with applications in Australian rainfall extremes
* PhD Thesis submitted October 2018, Graduation Ceremony April 2019

 <!-- * Postdoctoral research was on improving probabilistic forecasts of extreme weather events  -->
 <!-- * Core focus is on statistical post-processing methods for compound events forecasts -->
 
 <!-- * Core focus was on modelling rainfall extremes in continuous space with dependence -->
 <!-- * Applications considered in the thesis helped to improve our understanding of rainfall extremes in Australia --> 

# Employment and Education
```{r}
tribble(
    ~ uni, ~ degree, ~ loc, ~ dates, ~ details,
  
  "Lecturer (3 year fixed term contract)", 
  "Queensland University of Technology", 
  "Brisbane, Australia", 
  "Jan 2021 - Present", 
  "Currently lecturing Statistical Data Analysis (MXN500) and Quantitative Methods in Science (SEB113)",
  
  "Lecturer (3 year fixed term contract)", 
  "Queensland University of Technology", 
  "Brisbane, Australia", 
  "Jan 2021 - Present", 
  "As unit coordinator I have responsibility for the development, implementation and review of learning and teaching in these units",
  
   "Lecturer (3 year fixed term contract)", 
  "Queensland University of Technology", 
  "Brisbane, Australia", 
  "Jan 2021 - Present", 
  "Research Interests: Extreme Value Theory, Statistical Post-processing, Compound Risk Assessment,  Quality Control"
  
  ) %>% 
  detailed_entries(degree, dates, uni, loc, details)
```
```{r}
tribble(
    ~ uni, ~ degree, ~ loc, ~ dates, ~ details,
  
  "Postdoctoral Researcher", 
  "Delft University of Technology", 
  "Deflt, Netherlands", 
  "Oct. 2018 - Oct. 2020", 
  "Collaborated on a joint project with Koninklijk Nederlands Meteorologisch Instituut (KNMI)",
   "Postdoctoral Researcher", 
  "Delft University of Technology", 
  "Deflt, Netherlands", 
  "Oct. 2018 - Oct. 2020", 
  "Project Title: Probabilistic forecasts of extreme weather utilizing advanced methods from extreme value theory",
  
  "Postdoctoral Researcher", 
  "Delft University of Technology", 
  "Deflt, Netherlands", 
  "Oct. 2018 - Oct. 2020", 
  "Research Interests: Statistical Post-processing, Compound Events, Multivariate Weather Forecasting, Multivariate Scoring",
  
  "Postdoctoral Researcher", 
  "Delft University of Technology", 
  "Deflt, Netherlands", 
  "Oct. 2018 - Oct. 2020", 
  "Lectured Probability and Statistics for Aeronautical Engineers (WI2180LR-II)"

  ) %>% 
  detailed_entries(degree, dates, uni, loc, details)
```
```{r}
tribble(
    ~ uni, ~ degree, ~ loc, ~ dates, ~ details,
    
  "Doctor of Philosophy", "The University of Melbourne", "Melbourne, Australia", "Mar. 2014 - Oct. 2018", "Thesis Advisors: Prof. Peter Taylor, Prof. David Karoly and Dr. Alec Stephenson",
  "Doctor of Philosophy", "The University of Melbourne", "Melbourne, Australia", "Mar. 2014 - Oct. 2018", "Thesis Title: An Investigation of Australian Rainfall using Extreme Value Theory",
  "Doctor of Philosophy", "The University of Melbourne", "Melbourne, Australia", "Mar. 2014 - Oct. 2018", "Research Interests: Extreme Value Theory, Max-stable Processes, Rainfall Extremes, Extremal Dependence, Quality Control"
) %>% 
  detailed_entries(degree, dates, uni, loc, details)
```
```{r}
tribble(
    ~ uni, ~ degree, ~ loc, ~ dates, ~ details,
      
   "Graduate Researcher", 
  "Commonwealth Scientific Institue of Technology (CSIRO)", 
  "Melbourne, Australia", 
  "Feb. 2012 - Feb. 2014", 
  "Interested in using computational fluid dynamics for natural disaster modelling, ie. floods, tsnumais, storm  surge, sea level rise"
) %>% 
  detailed_entries(degree, dates, uni, loc, details)
```
```{r}
tribble(
    ~ uni, ~ degree, ~ loc, ~ dates, ~ details,
      
   "Bachelor of Science (Honours I in Mathematics)", "The University of Queensland", "Brisbane, Australia", "Jul. 2010 - Jun. 2011", "Thesis advisor: Prof. Tony Roberts",
  "Bachelor of Science (Honours I in Mathematics)", "The University of Queensland", "Brisbane, Australia", "Jul. 2010 - Jun. 2011", "Thesis title: Mean First Passage Time for Discrete Periodic Networks"
) %>% 
  detailed_entries(degree, dates, uni, loc, details)
```
```{r}
tribble(
    ~ uni, ~ degree, ~ loc, ~ dates, ~ details,
      
  "Bachelor of Science", "The University of Queensland", "Brisbane, Australia", "Feb. 2007 - Jun. 2010", "Major in mathematics"
 
) %>% 
  detailed_entries(degree, dates, uni, loc, details)
```

# Publications

```{r}
tribble(
   ~ what_title, ~ when_year, ~ with_journal, ~ where_status, ~ why_details,
  
  "Bottom-up identification of key elements of compound events",
  "2021",
  "Earth's Future",
  "Accepted with minor revisions",
  "E. Bevacqua, C. De Michele, C. Manning, A. Couasnon, A.F.S. Ribeiro, A.M. Ramos, E. Vignotto, A. Bastos, S. Blesic, F. Durante, J. Hillier, S.C. Oliveira, J.G. Pinto
E. Ragno, P. Rivoire, K.R. Saunders, K. Van Der Wiel, W. Wu, T. Zhang, J. Zscheischler",
  
  "Bottom-up identification of key elements of compound events",
  "2021",
  "Earth's Future",
  "Accepted with minor revisions",
  "Preprint: doi.org/10.1002/essoar.10507809.1"
 
 ) %>% 
  detailed_entries(
                 what = with_journal,
                 when = when_year, 
                 with = what_title,
                 where = where_status,
                 why = why_details)
```

```{r}
tribble(
   ~ what_title, ~ when_year, ~ with_journal, ~ where_status, ~ why_details,
  
  "Quality control and bias adjustment of crowd sourced wind speed observations",
  "2021",
  "Quarterly Journal of the Royal Meteorological Society",
  " ",
  "J. Chen, K. R. Saunders, and K. Whan",
  
  "Quality control and bias adjustment of crowd sourced wind speed observations",
  "2021",
  "Quarterly Journal of the Royal Meteorological Society",
  " ",
  "DOI: 10.1002/qj.4146"
 
 ) %>% 
  detailed_entries(
                 what = with_journal,
                 when = when_year, 
                 with = what_title,
                 where = where_status,
                 why = why_details)
```  
```{r}
tribble(
   ~ what_title, ~ when_year, ~ with_journal, ~ where_status, ~ why_details,
  
  "Redefining Southern Australia’s Climatic Regions and Seasons",
  "2021",
  "Journal of Southern Hemisphere Earth Systems Science", 
  "",
  "S. Fiddes, A. Pepler, K. R. Saunders, and P. Hope",
  
  "Redefining Southern Australia’s Climatic Regions and Seasons",
  "2021",
  "Journal of Southern Hemisphere Earth Systems Science", 
  "",
  "DOI: 10.1071/ES20003"

 ) %>% 
  detailed_entries(
                 what = with_journal,
                 when = when_year, 
                 with = what_title,
                 where = where_status,
                 why = why_details)
# need to check initials are correct
```  

```{r}
tribble(
  ~ what_title, ~ when_year, ~ with_journal, ~ where_status, ~ why_details,
 
  "Attribution of the Australian Bushfire Risk to Anthropogenic Climate Change",  
  "2021", 
  "Natural Hazards Earth System Sciences", 
  "",
  "G. J. van Oldenborgh, F. Krikken, S. Lewis, N. J. Leach, F. Lehner, K. R. Saunders, M. van Weele, K. Haustein, S. Li, et al.",
  
  "Attribution of the Australian Bushfire Risk to Anthropogenic Climate Change",
  "2021",
  "Natural Hazards Earth System Sciences",
  "",
  "DOI: 10.5194/nhess-21-941-2021"
 
 ) %>% 
  detailed_entries(what = with_journal,
                 when = when_year, 
                 with = what_title,
                 where = where_status,
                 why = why_details)
```  

```{r}
tribble(
  ~ what_title, ~ when_year, ~ with_journal, ~ where_status, ~ why_details,
  
  "A Regionalisation Approach for Rainfall based on Extremal Dependence",
  "2020",
  "Extremes",
  "", 
  "K.R. Saunders, A.G. Stephenson, AG and D.J. Karoly",
  
  "A Regionalisation Approach for Rainfall based on Extremal Dependence",
  "2020",
  "Extremes",
  "", 
  "DOI: 10.1007/s10687-020-00395-y"
  
 ) %>% 
  detailed_entries(what = with_journal,
                 when = when_year, 
                 with = what_title,
                 where = where_status,
                 why = why_details)
```
```{r}
tribble(
  ~ what_title, ~ when_year, ~ with_journal, ~ where_status, ~ why_details,    
  "An Investigation of Australian Rainfall Using Extreme Value Theory",
  "2018",
  "PhD Thesis",
  "",
  "K.R. Saunders", 
  
  "An Investigation of Australian Rainfall Using Extreme Value Theory",
  "2018",
  "PhD Thesis",
  "",
  "Identifier: http://hdl.handle.net/11343/220318"
) %>% 
  detailed_entries(what = with_journal,
                 when = when_year, 
                 with = what_title,
                 where = where_status,
                 why = why_details)
```  
  
```{r}
tribble(
  ~ what_title, ~ when_year, ~ with_journal, ~ where_status, ~ why_details,  
 "The Winning Entry for the EVA2017 Competition for Spatiotemporal Prediction of Extreme Rainfall using Generalized Extreme Value Quantiles", 
 "2018",
 "Extremes",
 "",
 "A.G. Stephenson, K. Saunders and L. Tafakori", 
 
  "The Winning Entry for the EVA2017 Competition for Spatiotemporal Prediction of Extreme Rainfall using Generalized Extreme Value Quantiles", 
 "2018",
 "Extremes",
 "",
 "DOI: 10.1007/s10687-018-0321-0") %>% 
  detailed_entries(what = with_journal,
                 when = when_year, 
                 with = what_title,
                 where = where_status,
                 why = why_details)
```  
  
```{r}
tribble(
  ~ what_title, ~ when_year, ~ with_journal, ~ where_status, ~ why_details,  
 "The Spatial Distribution of Rainfall Extremes and the Influence of El Niño Southern Oscillation",
  "2017",
 "Weather and Climate Extremes", 
 "",
 "K. Saunders, A.G. Stephenson, P.G. Taylor, and D. Karoly",  
 
 "The Spatial Distribution of Rainfall Extremes and the Influence of El Niño Southern Oscillation",
  "2017",
 "Weather and Climate Extremes", 
 "",
 "DOI: 10.1016/j.wace.2017.10.001"
) %>% 
  detailed_entries(what = with_journal,
                 when = when_year, 
                 with = what_title,
                 where = where_status,
                 why = why_details)
```  

```{r}
tribble(
  ~ what_title, ~ when_year, ~ with_journal, ~ where_status, ~ why_details, 

  "Assessing Sea Level Rise Risks to Coastal Floodplains in the Kakadu Region, Northern Australia, using a tidally-driven hydrodynamic model", 
  "2016",
  "Marine and Freshwater Research", 
  "",
  "P. Bayliss, K. Saunders, L. Dutra, L. Melo, J. Hilton, M. Prakash, F. Woolard", 
  
  "Assessing Sea Level Rise Risks to Coastal Floodplains in the Kakadu Region, Northern Australia, using a tidally-driven hydrodynamic model", 
  "2016",
  "Marine and Freshwater Research", 
  "",
  "DOI: 10.1071/MF16049" )  %>% 
  detailed_entries(what = with_journal,
                 when = when_year, 
                 with = what_title,
                 where = where_status,
                 why = why_details)
```  
 
```{r}
tribble(
  ~ what_title, ~ when_year, ~ with_journal, ~ where_status, ~ why_details,
  
  "Application of Smoothed Particle Hydrodynamics for Modelling Gated Spillway Flows",
  "2014",  
  "Applied Mathematical Modelling", 
  "", 
  "K. Saunders, M. Prakash, P.W. Cleary and M. Cordell", 
  
  "Application of Smoothed Particle Hydrodynamics for Modelling Gated Spillway Flows",
  "2014",  
  "Applied Mathematical Modelling", 
  "", 
  "DOI: 10.1016/j.apm.2014.05.008" ) %>% 
  detailed_entries(what = with_journal,
                 when = when_year, 
                 with = what_title,
                 where = where_status,
                 why = why_details)
```  

<!-- # Teaching Experience -->
<!-- ```{r} -->
<!-- tribble( -->
<!--   ~ position, ~ faculty, ~ location, ~ year, ~ details, -->

<!--   "Lecturer", -->
<!--   "Deflt Institute of Applied Mathematics", -->
<!--   "TU Delft", -->
<!--   "2019", -->
<!--   "WI2180LR-II Probability and Statistics for Aeronautical Engineers", -->
<!--   "Lecturer", -->
<!--   "Deflt Institute of Applied Mathematics", -->
<!--   "TU Delft", -->
<!--   "2019", -->
<!--   "Responsibilities included: Course development, assessment design, student consultation, collecting PRIME learning statistics" -->

<!-- ) %>%  -->
<!--   detailed_entries(faculty, year, position, location, details) -->

<!-- ```   -->
<!-- ```{r} -->
<!-- tribble( -->
<!--   ~ position, ~ faculty, ~ location, ~ year, ~ details, -->

<!--   "Sessional Tutor", -->
<!--   "School of Mathematics and Statistics", -->
<!--   "The University of Melbourne", -->
<!--   "2014 -- 2015", -->
<!--   "MAST20005 Statistics, MAST20004 Probability for statistics, MAST10006 Calculus 2" -->

<!-- ) %>%  -->
<!--   detailed_entries(faculty, year, position, location, details) -->

<!-- ``` -->
<!-- ```{r} -->
<!-- tribble( -->
<!--   ~ position, ~ faculty, ~ location, ~ year, ~ details, -->

<!--   # "College Tutor", -->
<!--   # "Newman College",  -->
<!--   # "The University of Melbourne", -->
<!--   # "2015", -->
<!--   # "Probability and Statistics tutor for undergraduate students", -->
<!--   #  -->
<!--   "Sessional Tutor", -->
<!--   "School of Mathematics and Physics", -->
<!--   "The University of Queensland", -->
<!--   "2007 -- 2011", -->
<!--   "MATH1061 Discrete Mathematics, MATH1051 Calculus and Linear Algebra, -->
<!--   MATH1050 Mathematical Foundations, MATH1040 Basic Mathematics" -->

<!-- ) %>%  -->
<!--   detailed_entries(faculty, year, position, location, details) -->

<!-- ``` -->

# Grants

```{r}
tribble(
 ~what_grant, ~ when_year, ~with_coapplicants, ~ where_fundingbody, ~ why_details,

  "First Byte ($10,000 AUD)", 
  "2021",
  "Applicants: Dr. Dr. Kate Saunders (QUT) to work jointly with researchers at the Bureau of Meteorology",
  "QUT Centre for Data Science",
  "Grant Title: Understanding the value of observations for wind forecasting on days  of high fire danger"
 
) %>% 
  detailed_entries(with_coapplicants, when_year, what_grant, where_fundingbody,
                   why_details) 
```

```{r}
tribble(
 ~what_grant, ~ when_year, ~with_coapplicants, ~ where_fundingbody, ~ why_details,

  "ACEMS Ideas Challenge ($10,000 AUD)", 
  "2021",
  "Applicants: Dr. Dr. Kate Saunders (QUT), Dr. Carolyn Huston (CSIRO) and Dr. Petra Kuhnert (CSIRO)",
  "ACEMS",
  "Grant Title: Complementing official wind records with crowd-sourced observations for improved forecasts of wind and fire behaviour",
 
   "ACEMS Ideas Challenge ($10,000 AUD)", 
  "2021",
  "Applicants: Dr. Dr. Kate Saunders (QUT), Dr. Carolyn Huston (CSIRO) and Dr. Petra Kuhnert (CSIRO)",
  "ACEMS",
  "This grant is to fund research between ACEMS researchers and industry partners"
 
) %>% 
  detailed_entries(with_coapplicants, when_year, what_grant, where_fundingbody,
                   why_details) 
```

```{r}
tribble(
 ~what_grant, ~ when_year, ~with_coapplicants, ~ where_fundingbody, ~ why_details,

  "Research Support Scheme ($15,000 AUD)", 
  "2020",
  "Applicants: Dr. Boris Beranger (UNSW), Dr. Kate Saunders (TU Delft) and Dr. Alec Stephenson (CSIRO)",
  "ACEMS",
  "Grant Title: Modelling of Environmental and Climate Extremes",
 
  "Research Support Scheme ($15,000 AUD)", 
  "2020",
  "Applicants: Dr. Boris Beranger (UNSW), Dr. Kate Saunders (TU Delft) and Dr. Alec Stephenson (CSIRO)",
  "ACEMS",
  "This grant is to foster collaboration between ACEMS Research Fellows and Associate Investigators",
 
  "Research Support Scheme ($15,000 AUD)", 
  "2020",
  "Applicants: Dr. Boris Beranger (UNSW), Dr. Kate Saunders (TU Delft) and Dr. Alec Stephenson (CSIRO)",
  "ACEMS",
  "As corona prevents international travel this funding initially went into stasis",
 
 "Research Support Scheme ($15,000 AUD)", 
  "2020",
  "Applicants: Dr. Boris Beranger (UNSW), Dr. Kate Saunders (TU Delft) and Dr. Alec Stephenson (CSIRO)",
  "ACEMS",
  "This funding has since been diverted to a research assistant due to rolling lockdowns"
 
) %>% 
  detailed_entries(with_coapplicants, when_year, what_grant, where_fundingbody,
                   why_details) 
```
```{r echo = FALSE, eval = FALSE}
tribble(
 ~what_grant, ~ when_year, ~with_coapplicants, ~ where_fundingbody, ~ why_details,

  "R Consortium Grant ($6,000 USD / $8,200 AUD)", 
  "2020",
  "Applicants: Dr. Jackon Kwok (UoM) and Dr. Kate Saunders (TU Delft)",
  "R Consortium",
  "Grant Title: Interactive Visualisations in R via R-to-JavaScript-transpilation",
  "R Consortium Grant ($6,000 USD / $8,200 AUD)", 
  "2020",
  "Applicants: Dr. Jackon Kwok (UoM) and Dr. Kate Saunders (TU Delft)",
  "R Consortium",
  "This grant funds the development of projects that help the R community",
  "R Consortium Grant ($6,000 USD / $8,200 AUD)", 
  "2020",
  "Applicants: Dr. Jackon Kwok (UoM) and Dr. Kate Saunders (TU Delft)",
  "R Consortium",
  "This is part one of a two part proposal",
  "R Consortium Grant ($6,000 USD / $8,200 AUD)", 
  "2020",
  "Applicants: Dr. Jackon Kwok (UoM) and Dr. Kate Saunders (TU Delft)",
  "R Consortium",
  "RConsortium has encouraged submission of the second part after the completion of the first set of milestones."
) %>% 
  detailed_entries(with_coapplicants, when_year, what_grant, where_fundingbody,
                   why_details) 
```

# Prizes
```{r}
tribble(
 ~what_prize, ~ when_year, ~with_coapplicants, ~ where_fundingbody, ~ why_details,

#  "Winner of the Harry Otten Prize in Meteorology",
#  "European Meteorological Society",
#  "1st prize: €25,500 ($40,000 AUD)",
#  "2021",
#  "Final announcement to be made at the September Meeting of the European Meteorolocial Society",

 "Harry Otten Prize: 1st place €25,500 ($40,000 AUD)",
 "2021",
 "Joint winner with Dr. Kirien Whan from KNMI",
 "European Meteorological Society",
 "A prize for innovation in meteorology",

 "Harry Otten Prize: 1st place €25,500 ($40,000 AUD)",
 "2021",
 "Joint winner with Dr. Kirien Whan from KNMI",
 "European Meteorological Society",
 "Project title: Second Wind - Extending the official wind gust record with citizen science observations",

  "Winner of the Young Statisticians Video Competition ($200 AUD)", 
# prize (€125)"",
  "2017",  
  "K.R. Saunders",
  "Statistics Society of Australia",
  "https://www.youtube.com/watch?v=88ZRYK0DmKs&ab_channel=KateSaunders",

  "Winning Team of the Data Challenge: Prediction of Extremal Precipitation",
  "2017",
  "A.G. Stephenson,  K.R. Saunders and L. Tafekori",
  "Extreme Value Analysis Conference, Delft",
  "Winning method was published: DOI: 10.1007/s10687-018-0321-0"

) %>%
  detailed_entries(with_coapplicants, when_year, what_prize, where_fundingbody,
                   why_details)
```

# Scholarships and Awards
```{r}
tribble(
 ~ award, ~ from, ~ amount, ~ dates, ~ details,
 
 "Postgraduate Researcher Award funded by a Laureate Fellowship",
 "The University of Melbourne",
 "$30,000 AUD per annum", #(~ €18,800 tax free)
 "2014 -- 2018",
 "Awarded in lieu of the Australian Postgraduate Award ($25,000 AUD per annum)",

  "Postgraduate Top Up Scholarship",
  "CSIRO",
  "$10,000 per annum", # (~ €6,265 tax free)",
  "2015 -- 2018",
  "Awarded to outstanding graduates to undertake postgraduate research",

  "Science Abroad Travelling Scholarship",
  "The University of Melbourne",
  "$1,500 AUD in total", # (~ €940 tax free)",
  "2016",
  "Awarded to outstanding graduates to undertake research abroad"

# {\bf The University of Queensland} \smallskip \\
# {\em Student Exchange Scholarship} (\$5,000 total) \hfill {2010}\\
# Awarded on the basis of academic merit to support a student exchange abroad \smallskip\\
# {\em Dean's Commendation, Faculty of Science} \hfill{2007 -- 2009} \\
# Awarded all eligible semesters for for academic excellence \smallskip\\
# {\em Summer Research Scholarship} (\$2,400 total) \hfill{2009} \\
# Awarded on the basis of academic merit to undertake an 8 week research project

) %>%
  detailed_entries(amount, dates, award, from, details)
```


# Supervision Experience
```{r}
tribble(
 ~what_student, ~ when_year, ~with_supervisors, ~ where_university, ~ why_details,

"Jiyeu Chen - Masters Thesis",#" (8 week project)", 
"2020",
"Primary Co-supervisors: Kate Saunders and Kirien Whan at KNMI, with University Co-Supervisor: Jason Frank",
"Utrecht University",
"Project Title: Quality control and verification of citizen science wind observations", 

"Jiyeu Chen - Masters Thesis",#" (8 week project)", 
"2020",
"Primary Co-supervisors: Kate Saunders and Kirien Whan at KNMI, with University Co-Supervisor: Jason Frank",
"Utrecht University",
"Paper accepted in the Quarterly Journal of the Royal Meteorlogical Society",

"Jiyeu Chen - Masters Thesis",#" (8 week project)", 
"2020",
"Primary Co-supervisors: Kate Saunders and Kirien Whan at KNMI, with University Co-Supervisor: Jason Frank",
"Utrecht University",
"KNMI also provided additional funding to produce a quality controlled dataset and an R Package") %>% 
  detailed_entries(with_supervisors, when_year, what_student, where_university,
                   why_details) 
```
```{r}
tribble(
 ~what_student, ~ when_year, ~with_supervisors, ~ where_university, ~ why_details,

"Kieran Maguire - Undergraduate Project",#" (8 week project)", 
"2016",
"Co-supervisors: Kate Saunders and Peter Taylor",
"The University of Melbourne",
"Project Title: Identifying spurious inhomogeneities in daily rainfall observations",
"Kieran Maguire - Undergraduate Project",#" (8 week project)", 
"2016",
"Co-supervisors: Kate Saunders and Peter Taylor",
"The University of Melbourne",
"The technical report from this project was shared with the Bureau of Meteorology") %>% 
  detailed_entries(with_supervisors, when_year, what_student, where_university,
                   why_details) 
```

```{r echo = FALSE, eval = FALSE}
tribble(
 ~what_student, ~ when_year, ~with_supervisors, ~ where_university, ~ why_details,

"Meng Shi - Undergraduate Project", # (4 week project)", 
"2012",
"Co-supervisors: Carolyn Huston and Kate Saunders",
"CSIRO",
"Project Title: A sensitivity analysis of tsunami inundation using a shallow water solver"


) %>% 
  detailed_entries(with_supervisors, when_year, what_student, where_university,
                   why_details) 
```

# Other Academic Activities

## Invited talks

<!-- Reply to Josh and accept talk -->
```{r}
tribble(
  ~what_seminar, ~when_year, ~with_inviter, ~where_location, ~why_details,
  
  "Spatial Extremes Session",
  "(Upcoming) December, 2021",
  "Computational and Methodological Statistics",
  "London and in hybrid",
  "Extreme Value Modelling of Compound Rainfall Extremes",
  
  "Bureau of Meteorology Research Seminar",
  "April, 2021",
  "Bureau of Meteorology",
  "Virtual",
  "Second Wind: Extending the official wind speed records with citizen science observations",
  
  "Machine Learning in the Netherlands (ML in NL) ",
  "April, 2020 (Cancelled Due to Corona)",
  "Picnic Data Science",
  "Amsterdam, Netherlands",
  "Examining our Implicit Assumptions when Clustering",

  "Newcastle Probabilty Seminar",
  "March, 2020 (Cancelled Due to Corona)",
  "Newcastle University",
  "Newcastle, UK",
  "Changing Spatial Dependence of Heatwaves",

  "Extremes TiDE Seminar Series",
  "February, 2019",
  "Tilburg University",
  "Tilburg, Netherlands",
  "A Regionalisation Approach for Extremes"

  ) %>%
   detailed_entries(with_inviter, when_year, what_seminar,
                    where_location, why_details)
```

## Workshop Organisation

<!-- Add in organisor for flood workshop -->
```{r}
tribble(
  ~what_workshop, ~when_year, ~with_attendees,
  ~where_venue, ~why_details,

  "Statistical Post-Processing Workshop",
  "2019",
  "Joint workshop between KNMI and TU Delft",
  "TU Delft, Netherlands",
  "Inaugural workshop designed to foster collaboration between statistics and climate researchers",

  "German Climate and Energy College Retreat",
  "2018",
  "Members of the Extended College Community",
  "Hidden Vale, Victoria",
  "A workshop to promote knowledge sharing between PhD students",

  "Applied Probability Group Retreat",
  "2017",
  "University of Melbourne Researchers",
  "Lorne, Victoria",
  "An internal workshop to share new research ideas in applied probability"

  ) %>%
   detailed_entries(with_attendees, when_year,
                    what_workshop, where_venue,
                    why_details)
```

## Journal Refereering
Weather and Climate Extremes, Environmetrics, Extremes, Spatial Statistics, Stochastic Networks

## Contribution to promoting women in STEM and general diversity

<!-- Add in moderator for the E & D panel  -->
```{r}
tribble(
  ~what_talk, ~when_year, ~with_invitee, ~where_location, ~why_details,

  "ACEMS Equity and Diversity Commitee",
  "2021",
  "Chair",
  "Australia",
  "ACEMS is underpinned by a commitment to equal opportunity and diversity",
  
  "Reboot STEMM Workshop",
  "2021",
  "Volunteer participant",
  "Virtual",
  "Involved in think-tank discussion with early- and mid-career researchers (EMCRs)",
  
   "Reboot STEMM Workshop",
  "2021",
  "Volunteer participant",
  "Virtual",
  "Helped co-design a strategy for a more inclusive and diverse way of defining, recognising and rewarding success",
  
  "An Introduction to Web Scraping using Rvest",
  "2019",
  "Invited presentation for R-Ladies Rotterdam",
  "Rotterdam, Netherlands",
  "R-Ladies’ is a diversity initiative, whose aim is to help empower underrepresented minorities within the R community.",

  "Women in mathematics panel discussion on affirmitive action",
  "2016",
  "Event Organiser and Panel Chair",
  "University of Melbourne",
  "International Womens' Day Event #BeBoldForChange",

# The School of Mathematics and Statistics made the bold decision last year to advertise and hire female only candidates. To celebrate this decision we will be holding a Q & A in the School of Mathematics and Statistics.
# In the Q & A we hope to bring light to some of the gender issues that were drivers behind the hiring decision, discuss the legalities and give people the opportunity to ask questions.

  "A Celebration of Dr. Alison Harcourt (Order of Australia)",
  "2015",
  "Event Joint Organiser with Gala Camacho Ferrari",
  "University of Melbourne",
  "Internation Womens' Day Event #MakeItHappen"

) %>%
   detailed_entries(with_invitee, when_year, what_talk, where_location, why_details)
```

## Mentoring
<!-- Could add in AMEG -->
<!-- volunteer speaker on the other panel -->
```{r}
tribble(
  ~what_talk, ~when_year, ~with_person, ~where_location,
  ~why_details,

  "Grabbing your Audience's Attention: Advice on Giving Talks",
  "2019",
  "ACEMS Seminar Series",
  "University of Melbourne",
  "Mentoring talk live streamed across ACEMS university nodes"
  #
  # "ACEMS Mentoring Program",
  # "2019",
  # "Mentor",
  # "Paired with an early stage PhD Student in Statistics at Monash University"

) %>%
   detailed_entries(with_person, when_year, what_talk, 
                   where_location, why_details)
```

## Other Committee Positions
```{r}
tribble(
  ~what_position, ~when_year, ~with_university, ~where_location, ~why_details,

  "Postgraduate Student President",
  "2015 -- 2016",
  "Statistics and Mathematics Student Society (STAMPS)",
  "University of Melbourne",
  "Some events run include: National Science Week Events, Careers Panel, Social Events"

) %>%
   detailed_entries(with_university, when_year,
                    what_position, where_location,
                    why_details)
```

# Outreach & Science Communication

## Art Exhibition

```{r}
tribble(
  ~what_name, ~when_year, ~with_collaborator, ~where_location, ~why_deatils,

  "ClimArt: R Package",
  "2019",
  "with Prof. David Karoly",
  "",
  "Produced code that visualises climate observations and how these observations are changing.",
  "ClimArt: R Package",
  "2019",
  "with Prof. David Karoly",
  "",
  "These visualisations were used in an exhibition called Climate Change versus Art."

) %>%
   detailed_entries(with_collaborator, when_year,  what_name, where_location, why_deatils)
```

## Popular Science Articles
```{r}
tribble(
  ~ authors, ~ year, ~ title, ~ blog, ~ stats,

  "K. Saunders and A.G. Stephenson",
  "2017",
  "Is Usain Bolt the greatest athlete of all time? That's not what the numbers say",
  "The Conversation",
   # \href{https://theconversation.com/is-usain-bolt-the-greatest-athlete-of-all-time-thats-not-what-the-numbers-say-82212}
  "Article statistics: 20,609 Readers, 275 Shares", #19 Tweets,

  "K. Saunders, D. Karoly and P.G. Taylor",
  "2015",
  # \href{https://theconversation.com/explainer-was-the-sydney-storm-once-in-a-century-40824}
  "Explainer: was the Sydney storm ‘once-in-a-century’?",
  "The Conversation",
  "Article statistics: 8591 Readers, 80 Shares" #24 Tweets,

) %>%
  detailed_entries(authors, year, title, blog, stats)
```

## Schools

```{r}
tribble(
  ~what_event, ~when_year, ~with_partner, ~where_location, ~why_details,

#   "Skype a Scientist",
#   "2020",
#   "Partner University ",
#   "Initiative to for XXX ",
  
  "Maths like a Mathematician",
  "2015 - 2017",
  "ACEMS Mathscraft",
  "Multiple locations",
  "Initiative to work with schools to teach mathematical style thinking to students",

  "Mathematicians in Schools",
  "2012 - 2013",
  "CSIRO Initiative",
  "Mentone Girls' Grammar School",
  "Presented my research in schools to help students understand how maths is used in the real world"

) %>%
   detailed_entries(with_partner, when_year, what_event,
                     where_location, why_details)
```

# Affiliations 

<!-- * Academic Collaborator with Koninklijk Nederlands Meteorologisch Instituut (KNMI) -->
* Member of the QUT Centre for Data Science
* Member of the European COST Action for compound events (Damocles)
* Associate Investigator with Australian Centre of Excellence in Mathematical and Statistical Frontiers (ACEMS)
* German Climate and Energy College (Alumni)

<!-- * Australian Women in Mathematics Special Interest Group (WIMSIG) (Past Member) -->
<!-- * Statistical Society of Australia: SSA (Past Member) -->
<!-- * Australian Mathematical Society (Past Member) -->

<!-- # Referees -->

<!-- Available upon request -->


