%!TEX TS-program = xelatex
%!TEX encoding = UTF-8 Unicode
% Awesome CV LaTeX Template for CV/Resume
%
% This template has been downloaded from:
% https://github.com/posquit0/Awesome-CV
%
% Author:
% Claud D. Park <posquit0.bj@gmail.com>
% http://www.posquit0.com
%
%
% Adapted to be an Rmarkdown template by Mitchell O'Hara-Wild
% 23 November 2018
%
% Template license:
% CC BY-SA 4.0 (https://creativecommons.org/licenses/by-sa/4.0/)
%


%-------------------------------------------------------------------------------
% CONFIGURATIONS
%-------------------------------------------------------------------------------
% A4 paper size by default, use 'letterpaper' for US letter
\documentclass[11pt, a4paper]{awesome-cv}

% Configure page margins with geometry
\geometry{left=1.4cm, top=.8cm, right=1.4cm, bottom=1.8cm, footskip=.5cm}

% Specify the location of the included fonts
\fontdir[fonts/]

% Color for highlights
% Awesome Colors: awesome-emerald, awesome-skyblue, awesome-red, awesome-pink, awesome-orange
%                 awesome-nephritis, awesome-concrete, awesome-darknight

\colorlet{awesome}{awesome-red}

% Colors for text
% Uncomment if you would like to specify your own color
% \definecolor{darktext}{HTML}{414141}
% \definecolor{text}{HTML}{333333}
% \definecolor{graytext}{HTML}{5D5D5D}
% \definecolor{lighttext}{HTML}{999999}

% Set false if you don't want to highlight section with awesome color
\setbool{acvSectionColorHighlight}{true}

% If you would like to change the social information separator from a pipe (|) to something else
\renewcommand{\acvHeaderSocialSep}{\quad\textbar\quad}

\def\endfirstpage{\newpage}

%-------------------------------------------------------------------------------
%	PERSONAL INFORMATION
%	Comment any of the lines below if they are not required
%-------------------------------------------------------------------------------
% Available options: circle|rectangle,edge/noedge,left/right

\name{Kate Saunders}{}

\position{Postdoctoral Researcher}
\address{Delft Institute of Applied Mathematics, TU Delft}

\mobile{+31 6 3374 7624}
\email{\href{mailto:K.R.Saunders@tudelft.nl}{\nolinkurl{K.R.Saunders@tudelft.nl}}}
\github{katerobsau}
\twitter{katerobsau}

% \gitlab{gitlab-id}
% \stackoverflow{SO-id}{SO-name}
% \skype{skype-id}
% \reddit{reddit-id}


\usepackage{booktabs}

% Templates for detailed entries
% Arguments: what when with where why
\usepackage{etoolbox}
\def\detaileditem#1#2#3#4#5{%
\cventry{#1}{#3}{#4}{#2}{\ifx#5\empty\else{\begin{cvitems}#5\end{cvitems}}\fi}}
\def\detailedsection#1{\begin{cventries}#1\end{cventries}}

% Templates for brief entries
% Arguments: what when with
\def\briefitem#1#2#3{\cvhonor{}{#1}{#3}{#2}}
\def\briefsection#1{\begin{cvhonors}#1\end{cvhonors}}

\providecommand{\tightlist}{%
	\setlength{\itemsep}{0pt}\setlength{\parskip}{0pt}}

%------------------------------------------------------------------------------



\begin{document}

% Print the header with above personal informations
% Give optional argument to change alignment(C: center, L: left, R: right)
\makecvheader

% Print the footer with 3 arguments(<left>, <center>, <right>)
% Leave any of these blank if they are not needed
% 2019-02-14 Chris Umphlett - add flexibility to the document name in footer, rather than have it be static Curriculum Vitae
\makecvfooter
  {July 2019}
    {Kate Saunders~~~·~~~Curriculum Vitae}
  {\thepage}


%-------------------------------------------------------------------------------
%	CV/RESUME CONTENT
%	Each section is imported separately, open each file in turn to modify content
%------------------------------------------------------------------------------



\section{About me}\label{about-me}

\begin{itemize}
\tightlist
\item
  Current research is in statistical post-processing
\item
  Core focus is on improving probabilistic forecasts of extreme weather
  events
\item
  PhD research was in extreme value theory
\item
  Core PhD focus was on modelling rainfall extremes in continuous space
  with dependence
\item
  Applications considered in the thesis helped to improve our
  understanding of rainfall extremes in Australia
\item
  Passionate about R programming and data visualisation
\end{itemize}

\section{Employment}\label{employment}

\detailedsection{\detaileditem{Delft University of Technology}{Oct. 2018 - Present}{Posdoctoral Researcher}{Deflt, Netherlands}{\item{Collaborating on a joint project with Koninklijk Nederlands Meteorologisch Instituut (KNMI)}\item{Research Interests: Post-processing for extreme events, compound events, modelling extremal dependence using covariates}}\detaileditem{Commonwealth Scientific Institue of Technology (CSIRO)}{Feb. 2012 - Feb. 2014}{Graduate Researcher}{Melbourne, Australia}{\item{Research Interests: natural disaster modelling, floods, tsnumais, sea level rise, computational fluid dynamics}}}

\section{Education}\label{education}

\detailedsection{\detaileditem{The University of Melbourne}{Mar. 2014 - Oct. 2018}{Doctor of Philosophy}{Melbourne, Australia}{\item{Thesis Advisors: Prof. Peter Taylor, Prof. David Karoly and Dr. Alec Stephenson}\item{Thesis Title: An Investigation of Australian Rainfall using Extreme Value Theory}\item{Research Interests: Extreme Value Theory, Statistics, Max-stable Processes, Rainfall Extremes, Extremal Dependence, Quality Control}}\detaileditem{The University of Queensland}{Jul. 2010 - Jun. 2011}{Bachelor of Science (Honours I in Mathematics)}{Brisbane, Australia}{\item{Thesis advisors: Prof. Tony Roberts}\item{Thesis title: Mean first passage time for discrete periodic networks}}\detaileditem{The University of Queensland}{Feb. 2007 - Jun. 2010}{Bachelor of Science}{Brisbane, Australia}{\item{Major in mathematics}}}

\section{Publications}\label{publications}

\detailedsection{\detaileditem{K.R. Saunders, A.G. Stephenson, AG and D.J. Karoly}{2019}{A Regionalisation Approach for Rainfall based on Extremal Dependence}{Extremes (in submission)}{\item{Preprint: https://arxiv.org/abs/1907.05750}}\detaileditem{K.R. Saunders}{2018}{An Investigation of Australian Rainfall Using Extreme Value Theory}{PhD Thesis}{\item{Identifier: http://hdl.handle.net/11343/220318}}\detaileditem{A.G. Stephenson, K. Saunders and L. Tafakori}{2018}{The Winning Entry for the EVA2017 Competition for Spatiotemporal Prediction of Extreme Rainfall using Generalized Extreme Value Quantiles}{Extremes}{\item{DOI: 10.1007/s10687-018-0321-0}}\detaileditem{K. Saunders, A.G. Stephenson, P.G. Taylor, and D. Karoly}{2017}{The Spatial Distribution of Rainfall Extremes and the Influence of El Niño Southern Oscillation}{Weather and Climate Extremes}{\item{DOI: 10.1016/j.wace.2017.10.001}}\detaileditem{P. Bayliss, K. Saunders, L. Dutra, L. Melo, J. Hilton, M. Prakash, F. Woolard}{2016}{Assessing Sea Level Rise Risks to Coastal Floodplains in the Kakadu Region, Northern Australia, using a tidally-driven hydrodynamic model}{Marine and Freshwater Research}{\item{DOI: 10.1071/MF16049}}\detaileditem{K. Saunders, M. Prakash, P.W. Cleary and M. Cordell}{2014}{Application of Smoothed Particle Hydrodynamics for Modelling Gated Spillway Flows}{Applied Mathematical Modelling}{\item{DOI: 10.1016/j.apm.2014.05.008}}}

\section{Popular Science Articles}\label{popular-science-articles}

\detailedsection{\detaileditem{K. Saunders and A.G. Stephenson}{2017}{Is Usain Bolt the greatest athlete of all time? That's not what the numbers say}{The Conversation}{\item{Article statistics: 20,609 Readers, 275 Shares}}\detaileditem{K. Saunders, D. Karoly and P.G. Taylor}{2015}{Explainer: was the Sydney storm ‘once-in-a-century’?}{The Conversation}{\item{Article statistics: 8591 Readers, 80 Shares}}}

\section{Scholarships and Awards}\label{scholarships-and-awards}

\detailedsection{\detaileditem{\$30,000 AUD per annum}{2014 -- 2018}{Laureate Fellowship Postgraduate Researcher Award}{The University of Melbourne}{\item{Awarded in lieu of the Australian Postgraduate Award (\$25,000 AUD per annum)}}}

\end{document}
